Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 introduction.tex
Added editorial comment about too many detector citations
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@871 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{Would the introduction be more effective without this paragraph?}
The coalescence of compact binary systems consisting of neutron stars (NS)
and/or black holes (BH) is the most promising source of gravitational radiation
for Advanced \LIGO~\cite{ALIGOWeb}, Virgo~\cite{AVirgoWeb}, \GEO~\cite{GEOWeb},
and \LCGT~\cite{LCGTWeb}.  Tens of binary coalescence events are expected to be
observed in the advanced detector era later this
decade~\cite{Abadie:2010p10836}.

>>>>

\editorial{Would the introduction be more effective without this paragraph?}
The coalescence of compact binary systems consisting of neutron stars (NS)
and/or black holes (BH) is the most promising source of gravitational radiation
for Advanced \LIGO~\cite{ALIGOWeb}, Virgo~\cite{AVirgoWeb}, \GEO~\cite{GEOWeb},%
\editorial{Can we condense all of the detector citations into one -- perhaps find a whitepaper?}%
and \LCGT~\cite{LCGTWeb}.  Tens of binary coalescence events are expected to be
observed in the advanced detector era later this
decade~\cite{Abadie:2010p10836}.
